Compositional Equivalences Based on Open pNets

### 2022-09-27 2016-Weak-FH-Bisim/WeakBisim.tex
example

\paragraph{pNets}
pNet is a convenient model to model concurrent systems in a hierarchical and parameterised way. The coordination between processes is expressed as synchronisation vectors that allow the definition of complex and expressive synchronisation patterns.
Open pNets are pNets for which some elements in the hierarchy are still undefined, such undefined elements are called \emph{holes}; a hole can be \emph{filled} later by providing another pNet.
This article first defines pNets and illustrates with an example how they can be used to provide the model of a communicating system.

\paragraph{A semantics for open pNets based on open automata}
The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter and no hole. Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a well-defined notion.

To define a semantics for open pNets we thus need LTSs that have both standard variable parameters, and process parameters, i.e.  holes that can be filled by processes. We call such LTSs with parameters and holes and equiped with a composition operation, \emph{open automata}. The main goal of this article is to define the theory behind open automata and to use them to provide a semantics and prove composition properties for open pNets.
  The transitions of open automata are much more complex than transitions of an LTS as the firing on a transition depends on parameters and actions that are symbolic. This article defines the notion of \emph{open transition} a transition that is symbolic in terms of parameters and coordinated actions.

@@

The behaviour of the pNet is defined with 
  synchronisation vectors also shown on the figure. In the examples, we write them on the form $<a,-,l>\to a$. This states that if the first hole $L$ performs the action $a$ and the third sub-net, i.e. the LTS, performs the action $l$, both of them progress synchronously, and an action $a$ is emitted by the pNet. $-$ denotes that the second hole does nothing. On the formal side, numbering and ordering the vectors is cumbersome, this is why we adopt indexed families of actions.
When encoding this operator, the LTS is sometimes called the ``control part'', it controls the evolution of the rest of the pNet. 
The first action  of one of  the holes decides which branch of the LTS is activated;
   all subsequent actions will be from the same side.

>>>>

\paragraph{pNets}
pNet is a convenient model to model concurrent systems in a hierarchical and parameterised way. The coordination between processes is expressed as synchronisation vectors that allow for the definition of complex and expressive synchronisation patterns.
Open pNets are pNets for which some elements in the hierarchy are still undefined, such undefined elements are called \emph{holes}. A hole can be \emph{filled} later by providing another pNet.
This article first defines pNets and illustrates with an example how they can be used to provide the model of a communicating system.

\paragraph{A semantics for open pNets based on open automata}
The semantics of pNets can be expressed as a translation to a labelled transition system (LTS), but only if the pNet has no parameter and no hole. Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a standard notion.

To define a semantics for open pNets we thus need LTSs that have both standard variable parameters, and process parameters, i.e.  holes that can be filled by processes. We call such LTSs with parameters and holes \emph{open automata}. The main goal of this article is to define the theory behind open automata and to use them to provide a semantics and prove compositionality properties for open pNets.
  The transitions of open automata are much more complex than transitions of an LTS as the firing of a transition depends on parameters and actions that are symbolic. This article defines the notion of \emph{open transition}, namely a transition that is symbolic in terms of parameters and coordinated actions.

@@

The behaviour of the pNet is defined with 
  synchronisation vectors also shown on the figure. In the examples, we write them on the form $<a,-,l>\to a$. This states that if the first hole $L$ performs the action $a$ and the third sub-net, i.e. the LTS, performs the action $l$, both of them progress synchronously, and an action $a$ is emitted by the pNet. The symbol $-$ at the second position denotes that the second hole does nothing. On the formal side, numbering and ordering the vectors is cumbersome, this is why we adopt indexed families of actions.
The LTS is sometimes called the ``control part'', it controls the evolution of the rest of the pNet. 
The first action  of one of  the holes decides which branch of the LTS is activated;
   all subsequent actions will be performed by the same side.
